B\'{e}zier $\bar{B}$ projection

### 2018-01-24 projection1120.tex
Another revision.

\paragraph{Remark} \added{From the stiffness matrix of the symmetric \Bezier $\bar{B}$ formulation \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, we can recover its mixed formulation as}

\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions }
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the conflict between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

>>>>

\paragraph{Remark} \added{ The symmetric \Bezier $\bar{B}$ formulation is not consistent with a mixed formulation. To see this we can recover the mixed formulation of \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, which is}
\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions }
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the inconsistency between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}
